---
title: "Lab 4"
author: "Krisztian Szavuly"
date: "February 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r}

# Setting global options

library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE
)

# we cannot override this below by chunks

```

## R Markdown

This is an *R Markdown document*. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
mean(cars$speed)
table(mtcars$am)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
plot(cars)
```

We can use a list:

* first element
* second element
* third element

Order list:

1. First element
2. Second element

## This is a header

### This is a subheader

##### Section title

This is the text of the section.

```{r pander-example, warning=FALSE}

library(pander)
pander(table(iris$Species))
pander(table(iris$Sepal.Width, by = iris$Species))

```

## Showing headers

We are loading a dataset with cars and check `r nrow(mtcars)` rows, where the number was inserted using in-line R code.

```{r header-example}

library(pander)
pander(head(mtcars))
pander(head(mtcars), emphasize.strong.rows(3))
pander(head(mtcars), emphasize.strong.cols(4))

```

``` {r shiny-example}

library(shiny)
inputPanel(
  sliderInput('n', label = 'Sample size',
              min = 1, max = 1000, value = 100,
              step = 10)
  )
  renderPlot({
    hist(runif(as.numeric(input$n)))
  })
```
